comgen-outline

### 2017-12-23 paper/appendix-bda.Rmd
improve causal expt figure; simulation figure

```{r genericsModelDiagram, fig.cap="Graphical model corresponding to the fully Bayesian data analysis of the RSA model. The feature-probability prior data $d^{pr}_{f}$ is assumed to be generated from the mixture model validated in Expt. 1a. The referent-category feature-probability $d^{pr}_{k,f}$ is generated from a latent feature-probability $h_{k,f}$. The fixed-threshold (control model) or uncertain-threshold RSA model takes the feature-probability prior $P_f(h)$, the referent-category feature-probability $h$, and a single speaker optimality parameter $\\lambda$ as input. This overall structured is repeated (except $\\lambda$) for each of the unique properties $f$ and categories $k$ that correspond to the generic sentences in our stimulus set. Note that RSA corresponds to a probabilistic *function* and not a *random variable* that is standard in graphical model notation; RSA cannot be represented by a graphical model because it has recursion. "}
knitr::include_graphics("figs/generics_bayesnetmodel.pdf", dpi = 108)
```

>>>>

```{r genericsModelDiagram, fig.cap="Graphical model corresponding to the fully Bayesian data analysis of the RSA model. The prevalence prior data $d^{pr}_{f}$ is assumed to be generated from the mixture model validated in Expt. 1a. The referent-category prevalence $d^{pr}_{k,f}$ is generated from a latent prevalence $p_{fk}$. The fixed-threshold (control model) or uncertain-threshold model take the prevalence priors $P_f(h)$, the referent-prevalence $h$, and a single speaker optimality parameter $\\lambda$ as input. This overall structured is repeated (except $\\lambda$) for each of the unique properties $f$ and categories $k$ that correspond to the generic sentences in our stimulus set. Note that S corresponds to a probabilistic *function* and not a *random variable* that is standard in graphical model notation; S cannot be represented by a graphical model because it has recursion. "}
knitr::include_graphics("figs/generics_bayesnetmodel.pdf", dpi = 108)
```

### 2017-12-23 paper/case3-causals.Rmd
improve causal expt figure; simulation figure

```{r causalExpt, fig.cap="Overview of Experiment 3. A: Results of previous experiments are shown one at a time. One of the results were lost. B: Particiapnts are asked to review results before continuing. C: Prior elicitation task. D: Causal endorsement task."}
knitr::include_graphics("figs/causal-expt.pdf", dpi = 108)
```

@@

causals.endorsement.insets <- cas.listener.predictions %>% 
    mutate(Parameter = factor(Parameter, 
                              levels = c("state_Prior","state_Posterior"),
                            labels = c("Prevalence prior (Expt. 3a)",
                                       "Interpreter model posterior")),
    Distribution = factor(distribution, 
                               levels = c("rare_weak",  "common_weak", "rare_deterministic", "common_deterministic"),
         labels = c("Weak, Rare", "Weak, Common", "Strong, Rare", "Strong, Common"))) %>%
  ggplot(., aes( x = value, fill = Distribution, color = Distribution, lty = Parameter, alpha = Parameter ))+
  geom_density(aes(y = ..scaled..), adjust = 1, size = 1)+
  facet_wrap(~Distribution, nrow = 2)+
  scale_fill_manual(values =inset.color.order )+
  scale_color_manual(values = inset.color.order)+
  scale_alpha_manual(values = c(0.8, 0.1))+
  scale_linetype_manual(values = c(1, 2))+
  scale_x_continuous(breaks = c(0, 1), limits= c(0, 1))+
  scale_y_continuous(breaks = c(0, 1), limits= c(0, 1))+
  xlab("Prevalence") +
  ylab("Scaled probability density")+
  theme(legend.position = "bottom", 
        legend.direction = 'vertical',
        legend.title = element_blank(),
        plot.margin = unit(c(16,6,6,6), "pt"))+
  guides(fill = F, color = F, alpha = F)

@@

```{r figure-causals, fig.width=9, fig.height=4, cache = T, fig.cap="Endorsing generalizations about causes. A: Endorsement model predictions (left) and human elicited endorsements (right) for four background distributions and two observed frequencies. B: Prevalence prior distributions and interpreter model posteriors upon hearing a causal generalization, for the experimentally manipulated priors. Endorsement mode predictions, interpreter model posteriors, and prevalence priors are inferred using both Expt. 3a and 3b data, following the same Bayesian data analytic approach outlined in Appendix C."}

>>>>

```{r causalExpt, fig.cap="Overview of Experiment 3. A-C: Results of previous experiments are shown one at a time, described in text and displayed in a table. One of the results was lost. Participants are asked to review previous results once all displayed. B: Prior elicitation task: Participants predict the results of the next 5 experiments. D: Causal endorsement task: Results of previously lost experiment are found and participants are asked to evaluate the causal generalization.", fig.width = 10}
caus.exp.1 <- ggdraw() + draw_image("figs/causal-expt-1.jpeg", scale = 1) +
  theme(plot.margin = unit(c(2,0,0,0), "pt")) 
caus.exp.2 <- ggdraw() + draw_image("figs/causal-expt-2.jpeg", scale = 1)+
  theme(plot.margin = unit(c(2,0,0,0), "pt")) 
caus.exp.3 <- ggdraw() + draw_image("figs/causal-expt-3.jpeg", scale = 1)+
  theme(plot.margin = unit(c(2,0,0,0), "pt")) 
caus.exp.4 <- ggdraw() + draw_image("figs/causal-expt-prior.jpeg", scale = 1)
caus.exp.5 <- ggdraw() + draw_image("figs/causal-expt-endorse.jpeg", scale = 1)

caus.exp.toprow <- plot_grid(caus.exp.1, caus.exp.2, caus.exp.3, labels = c("A", "B", "C"), nrow = 1, align = 'vh')

title <- ggdraw() + draw_label("Prevalence prior manipulation")
plot_grid(
  plot_grid(title, caus.exp.toprow, ncol=1, rel_heights=c(0.1, 1)),
  plot_grid(add_sub(caus.exp.4, "Prior elicitation"), add_sub(caus.exp.5,"Causal endorsement"), labels = c("D", "E"), nrow = 1),
  nrow = 2)
```

@@

causals.endorsement.insets <- cas.listener.predictions %>% 
    mutate(Parameter = factor(Parameter, 
                              levels = c("state_Prior","state_Posterior"),
                            labels = c("Prevalence prior (Expt. 3a)",
                                       "Interpreter model posterior")),
    Distribution = factor(distribution, 
                               levels = c("rare_weak",  "common_weak", "rare_deterministic", "common_deterministic"),
         labels = c("Weak, Rare", "Weak, Common", "Strong, Rare", "Strong, Common"))) %>%
  ggplot(., aes( x = value, fill = Distribution, color = Distribution, lty = Parameter, alpha = Parameter ))+
  geom_density(aes(y = ..scaled..), adjust = 1, size = 1)+
  facet_wrap(~Distribution, nrow = 2)+
  scale_fill_manual(values =inset.color.order )+
  scale_color_manual(values = inset.color.order)+
  geom_vline(xintercept = 0.2, lty = 3)+
  geom_vline(xintercept = 0.7, lty = 3)+
  scale_alpha_manual(values = c(0.8, 0.1))+
  scale_linetype_manual(values = c(1, 2))+
  scale_x_continuous(breaks = c(0, 1), limits= c(0, 1))+
  scale_y_continuous(breaks = c(0, 1), limits= c(0, 1))+
  xlab("Prevalence") +
  ylab("Scaled probability density")+
  theme(legend.position = "bottom", 
        legend.direction = 'vertical',
        legend.title = element_blank(),
        plot.margin = unit(c(16,6,6,6), "pt"))+
  guides(fill = F, color = F, alpha = F)

@@

```{r figure-causals, fig.width=9, fig.height=4, cache = T, fig.cap="Endorsing generalizations about causes. A: Endorsement model predictions (left) and human elicited endorsements (right) for four background distributions and two observed frequencies. B: Prevalence prior distributions and interpreter model posteriors upon hearing a causal generalization, for the experimentally manipulated priors. Vertical lines denote referent-prevalence levels for the causal endorsement task. Endorsement mode predictions, interpreter model posteriors, and prevalence priors are inferred using both Expt. 3a and 3b data, following the same Bayesian data analytic approach outlined in Appendix C."}

### 2017-12-23 paper/comgen-paper.Rmd
improve causal expt figure; simulation figure

s1.simulations.scatter <- ggplot(s1.simulations.relabeled, aes( x = featureProb, y = endorsement, fill = example))+
  geom_col(color = 'black')+
  # geom_label_repel(data = s1.simulations.relabeled, 
  #                  aes( label = example, fill = example),
  #                      color = 'white',
  #   box.padding = unit(0.0, "lines"),
  #   #point.padding = unit(1e-06, "lines"),
  #   segment.color = 'grey37')+
  scale_fill_solarized()+
  scale_x_continuous(limits = c(0, 1), 
                     breaks = c(0, 1))+
  scale_y_continuous(limits = c(-0.01, 1.01), 
                     breaks = c(0, 1),
                     labels = c("False", "True"))+
  #coord_fixed(ratio = 1)+
  coord_flip()+
  facet_grid(example~.)+
  guides(fill = F)+
  ylab("Endorsement")+xlab("Referent prevalence")+
  theme(strip.text.y = element_text(angle = 0, hjust = 0)
        #axis.title.x = element_text(hjust = 0)
        #axis.title.y = element_text(vjust = 0)
        )
  #ylab("Endorsement model prediction")+
  #xlab("Hypothesized prevalence")
```

```{r simulations, fig.cap = "Computational model behavior. A: Prior distributions over the prevalence of a feature in a category for 6 example features B: Different fixed thresholds (columns) give rise to different posterior interpretations. C: The interpreter model averages over all thresholds, producing posterior distributions that strongly depend upon the priors. D: Endorsement model predictions, assuming a particular referent-prevalence. Shapes of the priors were chosen to intuitivly correspond to properties labeling the distributions.", fig.width = 12, cache=F}
p1 <- fig.sims.priors +
  theme(plot.margin = unit(c(18,2,6,6), "pt")) #+ ggtitle("prevalence priors")
p2 <- fig.sims.fixed.thresholds +
  theme(plot.margin = unit(c(6,0,6,0), "pt")) + ylab("")
p3 <- fig.sims.uncertain.threshold+
  theme(plot.margin = unit(c(18,2,6,6), "pt"))+ 
    theme(strip.text.y = element_blank())#+ ggtitle("Interpreter model posterior")
p4 <- s1.simulations.scatter + theme(plot.margin = unit(c(18,0,6,6), "pt"))

prow <- plot_grid( p1 + theme(legend.position="none"),
           p2 + theme(legend.position="none"),
           p3 + theme(legend.position="none"),
           p4,
           align = 'vh',
           labels = c("A", "B", "C", "D"),
           hjust = -1,
           nrow = 1,
           #rel_widths = c(1.2, 3, 2)
           rel_widths = c(1.2, 3, 1.05, 1.7)
           )
prow
```

>>>>

s1.simulations.scatter <- ggplot(s1.simulations.relabeled, aes( x = featureProb, y = endorsement, fill = example))+
  geom_col(color = 'black')+
  # geom_label_repel(data = s1.simulations.relabeled, 
  #                  aes( label = example, fill = example),
  #                      color = 'white',
  #   box.padding = unit(0.0, "lines"),
  #   #point.padding = unit(1e-06, "lines"),
  #   segment.color = 'grey37')+
  scale_fill_solarized()+
  scale_x_continuous(limits = c(0, 1), 
                     breaks = c(0, 1))+
  scale_y_continuous(limits = c(-0.01, 1.01), 
                     breaks = c(0, 1),
                     labels = c("False", "True"))+
  #coord_fixed(ratio = 1)+
  coord_flip()+
  facet_grid(example~.)+
  guides(fill = F)+
  ylab("")+xlab("Referent prevalence")+
  theme(strip.text.y = element_text(angle = 0, hjust = 0)
        #axis.title.x = element_text(hjust = 0)
        #axis.title.y = element_text(vjust = 0)
        )
  #ylab("Endorsement model prediction")+
  #xlab("Hypothesized prevalence")
```

```{r simulations, fig.cap = "Computational model behavior. A: Prior distributions over the prevalence of a feature in a category for 6 example features B: Different fixed thresholds (columns) give rise to different partial interpretations. C: The interpreter model averages over all thresholds, producing posterior distributions that strongly depend upon the priors. D: Endorsement model predictions, assuming a particular referent-prevalence. Shapes of the priors were chosen to intuitivly correspond to properties labeling the distributions.", fig.width = 12, cache=F}
p1 <- fig.sims.priors +
  theme(plot.margin = unit(c(18,2,6,6), "pt")) #+ ggtitle("prevalence priors")
p2 <- fig.sims.fixed.thresholds +
  theme(plot.margin = unit(c(6,0,6,0), "pt")) + ylab("")
p3 <- fig.sims.uncertain.threshold+
  theme(plot.margin = unit(c(18,2,6,6), "pt"))+ 
    theme(strip.text.y = element_blank())#+ ggtitle("Interpreter model posterior")
p4 <- s1.simulations.scatter + theme(plot.margin = unit(c(18,0,6,6), "pt"))

prow <- plot_grid( 
  add_sub(p1 + theme(legend.position="none"), "Prevalence priors"),
  add_sub(p2 + theme(legend.position="none"), "Partial interpretations given fixed-thresholds"),
  add_sub(p3 + theme(legend.position="none"), "Full interpretations"),
  add_sub(p4, "Endorsement"),
           align = 'vh',
           labels = c("A", "B", "C", "D"),
           hjust = -1,
           nrow = 1,
           #rel_widths = c(1.2, 3, 2)
           rel_widths = c(1.2, 2.9, 1.15, 1.7)
           )
prow
```
